Storing messages with multipartite neural cliques

### 2014-07-18 Articles/article.tex
...

	Previous works (\cite{GriBer20114, GriBer20122}) considered the storage of binary constant weight codewords of weight $1$. We study the case of arbitrary weight. It is convenient to take $\mathcal{A}$ as the set of all binary constant weight codewords of weight $a$, where $a$ is a positive integer parameter which we will call number of activities. We set $m = | \mathcal{M} |$.

@@

	States of the network are characterized by which units are activated. A message corresponds to one, and only one, state of the network. A message $y$ of length $c$ can be seen as an array $x$ of length $c\dot l$ where for each $j\in [1,c]$, the $j$-th symbol of $y$ denoted $y_j$ is represented by $x[(j-1)l+1\hdots jl]$.\footnote{This is a clustered representation. $x$ is separated in $c$ clusters of $l$ units.} To sum up thje $k$-th unit in the $j$-th cluster corresponds to the index $l = (j-1)l+k$. We say the network is in state $x$ if for all $j\in [1, c]$ and $k\in [1,l]$, units $k$ in cluster $j$ of the network is active if, and only if, $x[(j-1)l+l] = 1$.

@@

	Storing a message $y$ in the network amounts to consider the network in state $x\,$%, that is for all $j$ and $k$ such as $1 \le k \le l$ and $1 \le j \le c$, the unit $k$ in the cluster $j$ is activated if and only if $x[(j-1)l+k] = 1$ 
	; then adding all connections between activated units excepting for units sharing the same cluster. Thus we obtain a multipartite clique between activated units representing a message.% The parameter $a$ describing the number of activated units per cluster will be called number of activities.

@@

	We can describe the network which is an undirected unweighted graph, by its adjacency matrix $W$. As for a message $x$, $x x^{\intercal}$ is the matrix describing the graph where all edges between active units exist, and only them, we can express $W$ in function of the following :

	$\tilde{W} = \max_{x\in \mathcal{M}} x x^{\intercal}$ which is the matrix where even edges between units in the same cluster have been added.
	$W$ can now be expressed as :\vspace*{1mm}

@@

		Intuitively the choice of $w = a$ is optimal (it it is the most natural one with $w = 1$ as well).
		Algorithm \ref{asumsum} is a description of the algorithm\footnote{No optimizations are described here (early stopping etc.)} :

@@

		At each step $t$, we compute the scores $s^{t} = \gamma \tilde{x^{t}} + W \tilde{x^{t}}$

		$\mbox{select}(w, v)$ is equal to the $w$-th greatest element of $v$ (counting repetitions).\footnote{$\mbox{select}(3, [3,2,1,2,0]) = 2$}

		$\tilde{x}^{t+1}_{(j-1)c+k} = \bigg \{
  			\begin{tabular}{ccc}
  			$1$ & if $s^t_{(j-1)c+k} \ge  \mbox{select}(w, (s^t_{(j-1)c+k'})_{1\le k' \le l})$ \\
  			$0$ & otherwise 
  		\end{tabular}
  		$

		\begin{algorithm}[!htb]
		\caption{$w$-sum of sum \label{asumsum}}
		\begin{algorithmic}[1]
		\Require{$v$ a binary array of length $n = c\cdot l$, $W$ the binary weight matrix representing the network, $S$ the number of iterations, $\gamma$ memory effect}
		\Procedure{Sum of sum}{$v, W, \gamma, S, w$}
		%\Statex
		\For{$s$ from $1$ to $S$}
		\State $s \gets \gamma v + W v$
		\For{$i$ from $1$ to $c$}
			\Let{treshold}{Select(s[$i$], $w$)} \Comment{Select(t, w) returns the element that would be in rank $w$ if the array t was sorted}
			\For{$j$ from $1$ to $l$}
			\Let{$v[i][j]$}{$s[i][j]$ $\ge$ treshold}
			\EndFor
		\EndFor
		\EndFor
		%\State\Return v
		\EndProcedure
		\end{algorithmic}
		\end{algorithm}

	We now study the performance of the new retrieving rule on distinct problems of retrieving messages : first partially erased messages, then erroneous messages, finally partially erased messages when the network has been damaged.

@@

	Messages will be considered as independent and identically distributed according to the uniform distribution.

@@

	%We generalise results on erasures obtained in \cite{GriBer20117} to multipartie cliques.
	Erasures of a symbol in a message corresponds to an erased cluster in the network. An erased cluster is a cluster of units which are all inactive, that is to mean set to $0$.

>>>>

	A binary constant weight code of weight $a$ is a code where all codewords have the same weight $a$, i.e. the same number of $1$ in them. Previous works (\cite{GriBer20114, GriBer20122}) considered the storage of binary constant weight codewords of weight $1$. We study the case of arbitrary weight. It is convenient to take $\mathcal{A}$ as the set of all binary constant weight codewords of length $l$ and of weight $a$, where $a$ is a positive integer parameter which we will call number of activities and which satisfies $a\le l$. We now have ${l \choose a} = |\mathcal{A}|$. We set $m = | \mathcal{M} |$.

@@

	States of the network are characterized by which units are activated. A message corresponds to one, and only one, state of the network. A message $y$ of length $c$ can be seen as an array $x$ of length $c\dot l$ where for each $j\in [1,c]$, the $j$-th symbol of $y$ denoted $y_j$ is represented by $x[(j-1)l+1\hdots jl]$.\footnote{This is a clustered representation. $x$ is separated in $c$ clusters of $l$ units.} To sum up the $k$-th unit in the $j$-th cluster corresponds to the index $l = (j-1)l+k$. We say the network is in state $x$ if for all $j\in [1, c]$ and $k\in [1,l]$, units $k$ in cluster $j$ of the network is active if, and only if, $x[(j-1)l+l] = 1$.

@@

	Storing a message $y$ in the network amounts to consider the network in state $x\,$%, that is for all $j$ and $k$ such as $1 \le k \le l$ and $1 \le j \le c$, the unit $k$ in the cluster $j$ is activated if and only if $x[(j-1)l+k] = 1$ 
	; then adding all edges between activated units to the network excepting for units sharing the same cluster. Note that edges already present in the network remain unchanged. Thus we obtain a multipartite clique between activated units representing a message.% The parameter $a$ describing the number of activated units per cluster will be called number of activities.

@@

	We can describe the network which is an undirected unweighted graph, by its adjacency matrix $W$. For a message $x$, $x x^{\intercal}$ is the matrix describing the graph where all edges between active units exist, and only them. Therefore we can express $W$ in function of the following :

	$\tilde{W} = \max_{x\in \mathcal{M}} x x^{\intercal}$ which is the matrix where all edges between units activated for each state $x$ in the same cluster have been added.
	$W$ can now be expressed as :\vspace*{1mm}

@@

		Intuitively the choice of $w = a$ is optimal (it it is the most natural one with $w = 1$ as well).
		%Algorithm \ref{asumsum} is a description of the algorithm\footnote{No optimizations are described here (early stopping etc.)} :

@@

		At each step $t$, we compute the scores, that is to mean the number of active units each unit is connected to, plus a memory effect $\gamma $ accounting for units begin already active. The array of scores at step $t$ is :  $s_{t} = \gamma \tilde{x_{t}} + W \tilde{x_{t}}$

		To detail the final step of the retrieving rule, we introduce a function $\mbox{select}$ such as for an array $v$, $\mbox{select}(w, v)$ is equal to the $w$-th greatest element of $v$ (counting repetitions).\footnote{$\mbox{select}(3, [3,2,1,2,0]) = 2$}

		\begin{align*}
		%$
		&\tilde{x}_{t+1}[(j-1)c+k] =\\ \bigg \{
  			&\begin{tabular}{ccc}
  			$1$ & if $s_t[(j-1)c+k] \ge  \mbox{select}(w, s_t[(j-1)l+1 \hdots jl)$ \\
  			$0$ & otherwise 
  		\end{tabular}
  		%$
  		\end{align*}

		We can for example fix a maximum number of steps to the algorithm or even stop at one point if $\tilde{x}_{t+1} = \tilde{x}_t$. The number of iterations can of course improve the retrieval rate.

%		\begin{algorithm}[!htb]
%		\caption{$w$-sum of sum \label{asumsum}}
%		\begin{algorithmic}[1]
%		\Require{$v$ a binary array of length $n = c\cdot l$, $W$ the binary weight matrix representing the network, $S$ the number of iterations, $\gamma$ memory effect}
%		\Procedure{Sum of sum}{$v, W, \gamma, S, w$}
%		%\Statex
%		\For{$s$ from $1$ to $S$}
%		\State $s \gets \gamma v + W v$
%		\For{$i$ from $1$ to $c$}
%			\Let{treshold}{Select(s[$i$], $w$)} \Comment{Select(t, w) returns the element that would be in rank $w$ if the array t was sorted}
%			\For{$j$ from $1$ to $l$}
%			\Let{$v[i][j]$}{$s[i][j]$ $\ge$ treshold}
%			\EndFor
%		\EndFor
%		\EndFor
%		%\State\Return v
%		\EndProcedure
%		\end{algorithmic}
%		\end{algorithm}

	We now study the performance of the new retrieving rule on distinct problems of retrieval : first partially erased messages, then erroneous messages.%, finally partially erased messages when the network has been damaged.

@@

	Messages will be considered as independent and identically distributed according to the uniform distribution. We compute theoretical error rates after one iteration of the retrieving rule. We compare those results to empirical error rates obtained through simulations. We also compare efficiencies of distinct networks for distinct values of the parameter $a$ (weight of the constant weight code) in the sense of information theory and show improvements over the case where $a = 1$.

@@

	%We generalise results on erasures obtained in \cite{GriBer20117} to multipartie cliques.

	Erasures of a symbol in a message corresponds to an erased cluster in the network. An erased cluster is a cluster of units which are all inactive, that is to mean set to $0$.
